---
title: "Viewshed Greenness Visibility Index"
author: "Azam Nezami"
date: "30/06/2024"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```


### Library

```{r}
library(terra)
library(sf)
library(sfheaders)
library(GVI)
library(classInt)
```


## DSM Lankelz neighborhood

```{r}
DSM_file_Lankelz <- "C:/Users/35266/Documents/ArcGIS/Projects/Thesis_GreenSpace/MOS_S_LA.tif"

# Read the raster file
raster_DSM_data_Lankelz <- rast(DSM_file_Lankelz)

# Assign LUREF Transverse Mercator CRS to the raster
crs(raster_DSM_data_Lankelz) <- crs("EPSG:2169") 

### Print information about the raster
print(raster_DSM_data_Lankelz)
plot(raster_DSM_data_Lankelz)
```


## DSM AlEsch and Brill neighborhoods

```{r}
DSM_file_AlEsch <- "C:/Users/35266/Documents/ArcGIS/Projects/Thesis_GreenSpace/MOS_S_ESCH.tif"

# Read the raster file
raster_DSM_data_AlESCH <- rast(DSM_file_AlEsch)

# Assign LUREF Transverse Mercator CRS to the raster
crs(raster_DSM_data_AlESCH) <- crs("EPSG:2169") 

### Print information about the raster
print(raster_DSM_data_AlESCH)
plot(raster_DSM_data_AlESCH)
```


## DSM Universiteit and Bruch neighborhoods

```{r}
DSM_file <- "C:/Users/35266/Documents/ArcGIS/Projects/MyProject1/Mos_BeBr_DSM.tif"

# Read the raster file
raster_DSM_data <- rast(DSM_file)

# Assign LUREF Transverse Mercator CRS to the raster
crs(raster_DSM_data) <- crs("EPSG:2169") 

### Print information about the raster
print(raster_DSM_data)
plot(raster_DSM_data)
```


### Resolution Equal(Universiteit and Bruch neighborhoods)

```{r}
res(raster_DSM_data)[1] == res(raster_DSM_data)[2] # This returns FALSE!!
```

```{r}
ext(raster_DSM_data)
```

```{r}
e <- round(ext(raster_DSM_data))
raster_DSM_data2 <- terra::rast(crs = crs(raster_DSM_data),
                   xmin =  e[1],
                   xmax = e[2],
                   ymin = e[3],
                   ymax = e[4],
                   resolution = 0.5)
raster_DSM_data2[] <- terra::values(raster_DSM_data, mat = FALSE)
```

```{r}
res(raster_DSM_data2)[1] == res(raster_DSM_data2)[2] # This returns TRUE
```
```{r}
### Print information about the raster
print(raster_DSM_data2)
plot(raster_DSM_data2)
```


## DTM All neighborhoods

```{r}
DTM_file <- "C:/Users/35266/Documents/ArcGIS/Projects/Thesis_GreenSpace/MOS_T_ALL.tif"

# Read the raster file
raster_DTM_data_ALL <- rast(DTM_file)
crs(raster_DTM_data_ALL) <- crs("EPSG:2169")

# Print information about the raster
print(raster_DTM_data_ALL)
plot(raster_DTM_data_ALL)
```


## Greenerry All neighborhoods

```{r}
Greenery_file <- "C:/Users/35266/Documents/ArcGIS/Projects/Thesis_GreenSpace/Reclass_G_All.tif"

# Read the raster file
raster_Greenery_data_All <- rast(Greenery_file)
crs(raster_Greenery_data_All) <- crs("EPSG:2169")

# Print information about the raster
print(raster_Greenery_data_All)
plot(raster_Greenery_data_All)

```


#### Single Observer in Universiteit and Bruch neighborhoods

```{r}

# Single Point
observer <- st_sf(sf_point(c(65550, 63035)), crs = st_crs(2169)) 

# Print information about the observer
print(observer)

```


#### Viewshed Analysis for a Single Observer in Universiteit and Bruch neighborhoods

```{r}
vs <- viewshed (observer = observer, dsm_rast = raster_DSM_data2 , dtm_rast = raster_DTM_data_ALL,
               max_distance = 50, observer_height = 1.7, plot = TRUE)

```


#### Viewshed green visibil Index for a Single Observer in Universiteit and Bruch neighborhoods

```{r}
vgvi_from_sf(observer = observer,
             dsm_rast = raster_DSM_data2, dtm_rast = raster_DTM_data_ALL, greenspace_rast = raster_Greenery_data_All,
             max_distance = 50, observer_height = 1.7,
             m = 0.5, b = 8, mode = "logit")$VGVI
```


## Calculate Greenery For Observers in Bruch neighborhood

```{r}
# Set the path to your CSV file Bruch
csv_file_path <- "D:/Thesis/Green_View/Observers/Observer_Bruch.csv"

# Read the CSV file into a data frame
Bruch_Points <- read.csv(csv_file_path)

# Specify the column names for X and Y coordinates
x_column_Bruch <- "X"
y_column_Bruch <- "Y"

# Create a simple feature object
observers_Bruch_11 <- st_as_sf(Bruch_Points, coords = c(x_column_Bruch, y_column_Bruch))

# Set the CRS if needed (replace EPSG:XXXX with the actual EPSG code)
observers_Bruch_11 <- st_set_crs(observers_Bruch_11, st_crs("EPSG:2169"))

```


## Viewshed green visibil Index for  Observers in Bruch neighborhood

```{r}
Result_Bruch <- vgvi_from_sf (observer = observers_Bruch_11,
             dsm_rast = raster_DSM_data2, dtm_rast = raster_DTM_data_ALL, greenspace_rast = raster_Greenery_data_All,
             max_distance = 50, observer_height = 1.7,
             m = 0.5, b = 8, mode = "logit")$VGVI
print(Result_Bruch)
```

```{r}
write.csv (Result_Bruch, file = "C:/Users/35266/Desktop/Green_Bruch")
```


## Calculate Greenery For Observers in Universiteit neighborhood

```{r}
# Set the path to your CSV file Belval
csv_file_path <- "D:/Thesis/Green_View/Observers/Observer_Universiteit.csv"

# Read the CSV file into a data frame
Universiteit_Points <- read.csv(csv_file_path)

# Specify the column names for X and Y coordinates
x_column_Universiteit <- "X"
y_column_Universiteit <- "Y"

# Create a simple feature object
observers_Universiteit_4 <- st_as_sf(Universiteit_Points, coords = c(x_column_Universiteit, y_column_Universiteit))

# Set the CRS if needed (replace EPSG:XXXX with the actual EPSG code)
observers_Universiteit_4 <- st_set_crs(observers_Universiteit_4, st_crs("EPSG:2169"))

```


## Viewshed green visibil Index for Observers in Universiteit neighborhood

```{r}
Result_Nuiversiteit <- vgvi_from_sf (observer = observers_Universiteit_4,
             dsm_rast = raster_DSM_data2, dtm_rast = raster_DTM_data_ALL, greenspace_rast = raster_Greenery_data_All,
             max_distance = 50, observer_height = 1.7,
             m = 0.5, b = 8, mode = "logit")$VGVI
print(Result_Nuiversiteit)
```

```{r}
write.csv (Result_Nuiversiteit, file = "C:/Users/35266/Desktop/Green_Universiteit")
```


## Calculate Greenery For Observers in Lankelz neighborhood

```{r}
# Set the path to your CSV file Lankelz
csv_file_path <- "D:/Thesis/Green_View/Observers/Observer_Lankelz.csv"

# Read the CSV file into a data frame
Lankelz_Points <- read.csv(csv_file_path)

# Specify the column names for X and Y coordinates
x_column_Lankelz <- "X"
y_column_Lankelz <- "Y"

# Create a simple feature object
observers_Lankelz_15 <- st_as_sf(Lankelz_Points, coords = c(x_column_Lankelz, y_column_Lankelz))

# Set the CRS if needed (replace EPSG:XXXX with the actual EPSG code)
observers_Lankelz_15 <- st_set_crs(observers_Lankelz_15, st_crs("EPSG:2169"))

```


## Viewshed green visibil Index for  Observers in Lankelz neighborhood

```{r}
Result_Lankelz <- vgvi_from_sf (observer = observers_Lankelz_15,
             dsm_rast = raster_DSM_data_Lankelz, dtm_rast = raster_DTM_data_ALL, greenspace_rast = raster_Greenery_data_All,
             max_distance = 50, observer_height = 1.7,
             m = 0.5, b = 8, mode = "logit")$VGVI
print(Result_Lankelz)
```

```{r}
write.csv (Result_Lankelz, file = "C:/Users/35266/Desktop/Green_Lankelz")
```


## Calculate Greenery For Observers in Al_Esch neighborhood

```{r}
# Set the path to your CSV file Al_Esch
csv_file_path <- "D:/Thesis/Green_View/Observers/Observer_Esch.csv"

# Read the CSV file into a data frame
Al_Esch_Points <- read.csv(csv_file_path)

# Specify the column names for X and Y coordinates
x_column_Esch <- "X"
y_column_Esch <- "Y"

# Create a simple feature object
observers_Esch_18 <- st_as_sf(Al_Esch_Points, coords = c(x_column_Esch, y_column_Esch))

# Set the CRS if needed (replace EPSG:XXXX with the actual EPSG code)
observers_Esch_18 <- st_set_crs(observers_Esch_18, st_crs("EPSG:2169"))

```


## Viewshed green visibil Index for  Observers in Al_Esch neighborhood

```{r}
Result_Esch <- vgvi_from_sf (observer = observers_Esch_18,
             dsm_rast = raster_DSM_data_AlESCH, dtm_rast = raster_DTM_data_ALL, greenspace_rast = raster_Greenery_data_All,
             max_distance = 50, observer_height = 1.7,
             m = 0.5, b = 8, mode = "logit")$VGVI
print(Result_Esch)
```

```{r}
write.csv (Result_Esch, file = "C:/Users/35266/Desktop/Green_Esch")
```


## Calculate Greenery For Observers in Brill neighborhood

```{r}
# Set the path to your CSV file Brill
csv_file_path <- "D:/Thesis/Green_View/Observers/Obeserver_Brill.csv"

# Read the CSV file into a data frame
Brill_Points <- read.csv(csv_file_path)

# Specify the column names for X and Y coordinates
x_column_Brill <- "X"
y_column_Brill <- "Y"

# Create a simple feature object
observers_Brill_13 <- st_as_sf(Brill_Points, coords = c(x_column_Brill, y_column_Brill))

# Set the CRS if needed (replace EPSG:XXXX with the actual EPSG code)
observers_Brill_13 <- st_set_crs(observers_Brill_13, st_crs("EPSG:2169"))

```


## Viewshed green visibil Index for  Observers in Brill neighborhood

```{r}
Result_Brill <- vgvi_from_sf (observer = observers_Brill_13,
             dsm_rast = raster_DSM_data_AlESCH, dtm_rast = raster_DTM_data_ALL, greenspace_rast = raster_Greenery_data_All,
             max_distance = 50, observer_height = 1.7,
             m = 0.5, b = 8, mode = "logit")$VGVI
print(Result_Brill)
```

```{r}
write.csv (Result_Brill, file = "C:/Users/35266/Desktop/Green_Brill")
```




